Untitled

### 2016-09-23 Rmd/analyze.Rmd
link NPQ capacity to photochemistry

```{r initialize, include=FALSE}
# Initialize SU function
synth <- function(x, y, m) 1/((1/m)+(1/x)+(1/y)-(1/(x+y)))
# Source default parameters and functions
sapply(list.files(path="R", pattern="*.R", full.names=T), source, .GlobalEnv)
```

@@

# Initialize environment
env <- init_env(time=time, L=c(10,40,2), N=c(1e-7,1e-7,0), X=c(0,0,0))

# Set parameters
pars <- def_pars()  # Get default parameters
#pars$rpars$gammaR <- 0.03  # Change any default parameters

@@

##### Plot run 1 symbiont PI curve
```{r run1_PI, fig.height=1}
sym_PI(pars)
```

@@

#### Run 1 with no symbiont recycling
```{r runNR_plots}
parsNR <- pars
parsNR$spars$sigmaNS <- 0
parsNR$spars$sigmaCS <- 0
runNR <- run_coral(time=time, env=env, pars=parsNR)
plot_run(runNR)
with(runNR, {

})
```

#### Compare amount of recycled sym nitrogen between runs
```{r compareN}
proprNS <- run$S$rNS / (run$S$rNS + run$H$rhoN*run$H$H/run$S$S)
par(mfrow=c(2,1))
plot(time, proprNS)
proprNS <- runNR$S$rNS / (runNR$S$rNS + runNR$H$rhoN*runNR$H$H/runNR$S$S)
plot(time, proprNS)

proprCS <- run$S$rCS / (run$S$rCS + run$H$jCO2*run$H$H/run$S$S)
par(mfrow=c(2,1))
plot(time, proprCS)
proprCS <- runNR$S$rCS / (runNR$S$rCS + (runNR$H$rCH + runNR$H$jCO2)*runNR$H$H/runNR$S$S)
plot(time, proprCS)
```

### Run 2 - tolerant symbiont
```{r run2, echo=F}
pars2 <- pars
pars2$spars$kROS <- 80
pars2$spars$jCPm <- 1.4

run2 <- run_coral(time=time, env=env, pars=pars2)
```

##### Plot symbiont PI curve
```{r run2_PI, fig.height=2}
sym_PI(pars2)
```

##### Plot run 2 output
```{r run2_plots}
plot_run(run2)
```

##### Increase light to bleach tolerant symbiont
```{r}
env <- init_env(time=time, L=c(10,60,2), N=c(1e-7,1e-7,0), X=c(0,0,0))
run <- run_coral(time=time, env=env, pars=pars2)
plot_run(run)
```

>>>>

```{r initialize, include=FALSE}
# Initialize SU function
synth <- function(x, y, m) 1/((1/m)+(1/x)+(1/y)-(1/(x+y)))
# Source default parameters and functions
sapply(c("R/conversions.R", "R/def_pars.R", "R/init_env.R", "R/plot_results.R",
         "R/run_coral.R", "R/sym_PI.R"), source, .GlobalEnv)
```

@@

# Initialize environment
env <- init_env(time=time, L=c(20,32,2), N=c(1e-6,1e-6,0), X=c(0,0,0))

# Set parameters
pars <- def_pars()  # Get default parameters
#pars$rpars$gammaR <- 0.03  # Change any default parameters
#pars$jCO2a <- 1
#pars$jCO2a <- 0.1

@@

##### Plot run 1 symbiont PI curve
```{r run1_PI, fig.height=1}
#sym_PI(pars)
```

@@

##### Run 2 -- increase jCO2a
```{r run2_plots}
pars2 <- pars
pars2$jCO2a <- 10
run2 <- run_coral(time=time, env=env, pars=pars2)
plot_run(run2)
